%──────────────────────────────────────────────────────────────────────────────
%  Liam Wood — Resume
%  Target: Senior Platform / Infrastructure Engineer — Startups
%  (Databricks, Anduril, Rippling, Fly.io, Modal, Figma)
%──────────────────────────────────────────────────────────────────────────────
\documentclass[10pt, letterpaper]{article}

\usepackage[top=0.45in, bottom=0.45in, left=0.65in, right=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

%── Colours ───────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{1A1A2E}
\definecolor{rule}{HTML}{888888}

%── Section style ─────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}\uppercase}
  {}{0em}{}
  [\vspace{-4pt}\textcolor{rule}{\hrule height 0.5pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{8pt}{2pt}

%── List style ────────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=0pt,
  parsep=0pt,
  topsep=1pt,
  label=\textbullet
}

%── Helpers ───────────────────────────────────────────────────────────────────
\newcommand{\job}[3]{%
  \noindent\textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\pagestyle{empty}

%──────────────────────────────────────────────────────────────────────────────
\begin{document}

%── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{accent} Liam Wood}\\[4pt]
  Austin, TX \;|\;
  \href{tel:13057909093}{(305) 790-9093} \;|\;
  \href{mailto:general.lvwood@gmail.com}{general.lvwood@gmail.com}
\end{center}

\vspace{1pt}

%── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\job{Microsoft}{Software Engineer II — Infrastructure \& Scale, Notifications Service {\normalfont\textit{(promoted year-over-year)}}}{July 2022 – Present}
\begin{itemize}
  \item Sole infrastructure owner for the \textbf{OneDrive/SharePoint Notifications Service}
    — \textbf{6B+ events/month} across \textbf{M365, Teams, Viva, Whiteboard}, and dozens
    of Microsoft products; globally deployed to every geo, operated end-to-end.
  \item Drove full platform migration: \textbf{Azure Cloud Services → Service Fabric → AKS}
    without a single dropped message; halved compute footprint, saving \textbf{\$750K annually};
    implemented \textbf{CPU-based KEDA autoscaling} that handled live traffic-spike incidents.
  \item First to ship \textbf{heuristic-based spam blocks} on the policy engine; blocked
    \textbf{tens of millions of spam events} with zero impact to live traffic; own hourly
    deployments to internal test ring for partner validation before production.
  \item Moved from slot-based to \textbf{in-place deployments} via custom \textbf{ADO YAML
    hotfix pipeline}; cut deployment latency from \textbf{30+ days to under 10 days}
    while maintaining global safe deployment practices across all geos.
  \item Designed \textbf{BCDR automatic failover} (FrontDoor weighted endpoints), cert
    \textbf{autorotation with SNI auth}, \textbf{KeyVault}-based Service Bus message encryption,
    and secret expiration alerting; maintained \textbf{99.99\% availability} worldwide.
\end{itemize}

\vspace{2pt}

\job{Visa}{Senior Software Engineer — Clearing \& Settlement Infrastructure {\normalfont\textit{(promoted in 1.25 years)}}}{October 2020 – July 2022}
\begin{itemize}
  \item Redesigned \textbf{settlement management system in C++} end-to-end — real-time global
    comms between \textbf{IBM z/OS mainframes}; full technical ownership, no oversight.
  \item Pioneered \textbf{git adoption on the IBM mainframe} using Broadcom Git Bridge;
    developed \textbf{C++ Kafka prototype} for streaming mainframe transactional data to Linux.
\end{itemize}

\vspace{2pt}

\job{Digital Worlds Institute — University of Florida}{Software Developer}{August 2019 – February 2020}
\begin{itemize}
  \item \textbf{Sole developer}: blockchain + AR web card game — \textbf{Node.js} backend,
    Vue.js frontend, SQLite; blockchain for public reward records, AR for in-game asset display.
\end{itemize}

%── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\noindent\textbf{University of Florida} \hfill \textit{August 2018 – May 2022}\\
B.S.\ Computer Science

%── Skills ────────────────────────────────────────────────────────────────────
\section{Skills}

\noindent
\begin{tabular}{@{}p{2.0in}p{4.7in}}
  \textbf{Languages}          & C++, Python, C\#/.NET, Node.js, JavaScript \\[2pt]
  \textbf{Infrastructure}     & AKS, Kubernetes, KEDA, Azure Service Fabric, Azure FrontDoor,
                                Azure KeyVault, Azure DevOps, Terraform, Helm \\[2pt]
  \textbf{Distributed Systems}& High-scale event processing, Kafka, message encryption,
                                multi-region failover, BCDR, queue-based scheduling \\[2pt]
  \textbf{Reliability}        & Cert autorotation (SNI), secret management, in-place deployments,
                                spam/abuse policy, SLOs, on-call, incident response \\
\end{tabular}

\end{document}
