%──────────────────────────────────────────────────────────────────────────────
%  Liam Wood — Resume
%  Target: Senior Platform Infrastructure Engineer, Citadel Securities
%──────────────────────────────────────────────────────────────────────────────
\documentclass[11pt, letterpaper]{article}

\usepackage[top=0.55in, bottom=0.55in, left=0.70in, right=0.70in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

%── Colours ───────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{1A1A2E}   % near-black navy
\definecolor{rule}{HTML}{888888}

%── Section style ─────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}\uppercase}
  {}{0em}{}
  [\vspace{-4pt}\textcolor{rule}{\hrule height 0.5pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{10pt}{4pt}

%── List style ────────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt,
  label=\textbullet
}

%── Helpers ───────────────────────────────────────────────────────────────────
% \job{Company}{Title}{Date range}
\newcommand{\job}[3]{%
  \noindent\textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\pagestyle{empty}

%──────────────────────────────────────────────────────────────────────────────
\begin{document}

%── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{accent} Liam Wood}\\[4pt]
  Austin, TX \;|\;
  \href{tel:13057909093}{(305) 790-9093} \;|\;
  \href{mailto:general.lvwood@gmail.com}{general.lvwood@gmail.com}
\end{center}

\vspace{2pt}

%── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\job{Microsoft}{Software Engineer II — Platform Infrastructure}{July 2022 – Present}
\begin{itemize}
  \item Own design and end-to-end reliability of distributed notification infrastructure
    processing \textbf{6B+ events/month} across OneDrive and SharePoint, spanning dozens of
    interdependent services deployed across Linux-hosted AKS clusters.
  \item Architected \textbf{KEDA-driven job scheduling and autoscaling} system tied to real-time
    queue depth and traffic patterns, reducing tail latency and eliminating
    over-provisioning waste (\$500k–\$750k annual savings).
  \item Led AKS migration and full \textbf{deployment and configuration management}
    re-architecture — redesigned infra-as-code pipelines and cluster provisioning to
    support safe, repeatable deployments at scale.
  \item Designed \textbf{multi-region failover} architecture using Azure FrontDoor and Traffic
    Manager; maintained \textbf{99.99\% availability} under continuous global load with automated
    BCDR failover runbooks.
  \item Owned \textbf{CI/CD pipelines} (Azure DevOps, Git) and progressive rollout tooling,
    improving release cadence from 6-week cycles to \textbf{weekly deployments} with integrated
    smoke testing and automated rollback.
  \item Built and maintained \textbf{process state observability} systems and incident dashboards;
    collaborated with SRE teams to define alerting thresholds, runbooks, and on-call
    escalation paths.
  \item Collaborated with partner engineering teams worldwide to safely enable new
    customer-facing notification features, driving requirements through design, testing,
    and staged rollout.
  \item Promoted twice in 3 years for technical leadership across reliability engineering,
    cost optimization, and deployment safety.
\end{itemize}

\vspace{4pt}

\job{Visa}{Senior Software Engineer — Clearing \& Settlement Infrastructure}{October 2020 – July 2022}
\begin{itemize}
  \item Designed and implemented \textbf{state-machine–driven settlement engine components}
    in Python and C++, processing \textbf{trillions in annual transaction volume} across
    distributed financial infrastructure with strict correctness and consistency guarantees.
  \item Engineered distributed systems requiring \textbf{fault-tolerant, exactly-once processing}
    under concurrent load; contributed to early real-time transaction observability and
    analysis pipelines across clearing and settlement systems.
  \item Built and maintained comprehensive \textbf{unit and integration test suites} for
    high-criticality financial infrastructure, ensuring correctness and catch-all coverage
    for edge cases in concurrent transaction flows.
  \item Operated within a strict \textbf{Linux-based production environment}; routinely diagnosed
    and resolved complex distributed system failures under time pressure with direct
    financial impact.
\end{itemize}

\vspace{4pt}

\job{Digital Worlds Institute — University of Florida}{Software Developer}{August 2019 – February 2020}
\begin{itemize}
  \item Sole developer for a browser-based AR/blockchain card game platform; built a
    \textbf{Node.js backend} with Redis pub/sub managing \textbf{100+ concurrent WebSocket connections}
    and real-time distributed game state synchronization.
  \item Designed frontend in Vue.js with native-like performance and integrated WebAR
    libraries, delivering a full-stack production system end-to-end.
\end{itemize}

%── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\noindent\textbf{University of Florida} \hfill \textit{August 2016 – May 2020}\\
B.S.\ Computer Science\\[2pt]
Vice President, GatorVR — led technical workshops and mentored students in VR/AR
development and CS fundamentals.

%── Skills ────────────────────────────────────────────────────────────────────
\section{Skills}

\noindent
\begin{tabular}{@{}p{2.2in}p{4.5in}}
  \textbf{Languages}          & C++, Python, C\#/.NET, Node.js, JavaScript \\[2pt]
  \textbf{Infrastructure}     & Linux (AKS/bare-metal), Kubernetes, KEDA, Azure FrontDoor,
                                Azure DevOps, BCDR Planning \\[2pt]
  \textbf{Distributed Systems}& High-scale event processing, multi-region failover,
                                fault-tolerant state machines, queue-based scheduling \\[2pt]
  \textbf{SDLC \& Tooling}    & Git, Azure DevOps CI/CD, Jenkins-equivalent pipelines,
                                progressive rollout, integration \& regression testing \\[2pt]
  \textbf{Observability}      & Process state monitoring, alerting design, incident
                                response, SRE collaboration \\
\end{tabular}

\end{document}
