%──────────────────────────────────────────────────────────────────────────────
%  Liam Wood — Resume
%  Target: Infrastructure / Systems Engineer — Finance & HFT
%  (Jane Street, Two Sigma, Jump Trading, HRT, Citadel)
%──────────────────────────────────────────────────────────────────────────────
\documentclass[11pt, letterpaper]{article}

\usepackage[top=0.55in, bottom=0.55in, left=0.70in, right=0.70in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

%── Colours ───────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{1A1A2E}
\definecolor{rule}{HTML}{888888}

%── Section style ─────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}\uppercase}
  {}{0em}{}
  [\vspace{-4pt}\textcolor{rule}{\hrule height 0.5pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{10pt}{4pt}

%── List style ────────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt,
  label=\textbullet
}

%── Helpers ───────────────────────────────────────────────────────────────────
\newcommand{\job}[3]{%
  \noindent\textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\pagestyle{empty}

%──────────────────────────────────────────────────────────────────────────────
\begin{document}

%── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{accent} Liam Wood}\\[4pt]
  Austin, TX \;|\;
  \href{tel:13057909093}{(305) 790-9093} \;|\;
  \href{mailto:general.lvwood@gmail.com}{general.lvwood@gmail.com}
\end{center}

\vspace{2pt}

%── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\job{Visa}{Senior Software Engineer — Clearing \& Settlement Infrastructure}{October 2020 – July 2022}
\begin{itemize}
  \item Designed and implemented \textbf{state-machine–driven settlement engine components}
    in \textbf{C++ and Python}, processing \textbf{trillions in annual transaction volume}
    across distributed financial infrastructure with strict correctness and consistency guarantees.
  \item Engineered distributed systems requiring \textbf{fault-tolerant, exactly-once processing}
    under concurrent load; contributed to real-time transaction observability and analysis
    pipelines across clearing and settlement systems.
  \item Built comprehensive \textbf{unit and integration test suites} for high-criticality
    financial infrastructure, ensuring correctness and full edge-case coverage for
    concurrent transaction flows.
  \item Operated within a strict \textbf{Linux-based production environment}; diagnosed and
    resolved complex distributed system failures under time pressure with direct
    financial impact.
\end{itemize}

\vspace{4pt}

\job{Microsoft}{Software Engineer II — Platform Infrastructure {\normalfont\textit{(promoted twice in 3 years)}}}{July 2022 – Present}
\begin{itemize}
  \item Own design and end-to-end reliability of distributed notification infrastructure
    processing \textbf{6B+ events/month} across OneDrive and SharePoint, spanning dozens of
    interdependent services on Linux-hosted AKS clusters.
  \item Designed \textbf{multi-region failover} architecture; maintained \textbf{99.99\% availability}
    under continuous global load with automated BCDR runbooks and on-call rotation.
  \item Architected \textbf{KEDA-driven autoscaling} tied to real-time queue depth; reduced
    tail latency and eliminated over-provisioning (\$500k–\$750k annual savings).
  \item Led full \textbf{AKS migration} — authored \textbf{Terraform} modules for cluster
    provisioning and \textbf{Helm}-managed workload deployment; rebuilt infra-as-code
    pipelines for safe, repeatable deploys at scale.
  \item Built observability stack (Azure Monitor, Grafana, OpenTelemetry); defined SLOs,
    alerting thresholds, distributed tracing, and runbooks with SRE teams.
\end{itemize}

\vspace{4pt}

\job{Digital Worlds Institute — University of Florida}{Software Developer}{August 2019 – February 2020}
\begin{itemize}
  \item Built \textbf{C++ and Python} systems infrastructure; developed concurrent data pipelines
    and low-level tooling in a Linux production environment.
\end{itemize}

%── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\noindent\textbf{University of Florida} \hfill \textit{August 2018 – May 2022}\\
B.S.\ Computer Science

%── Skills ────────────────────────────────────────────────────────────────────
\section{Skills}

\noindent
\begin{tabular}{@{}p{2.2in}p{4.5in}}
  \textbf{Languages}          & \textbf{C++}, Python, C\#/.NET, Node.js, JavaScript \\[2pt]
  \textbf{Distributed Systems}& Fault-tolerant state machines, exactly-once processing,
                                multi-region failover, high-scale event processing,
                                queue-based scheduling \\[2pt]
  \textbf{Infrastructure}     & Linux (AKS/bare-metal), Kubernetes, KEDA, Terraform, Helm \\[2pt]
  \textbf{Correctness \& Testing} & Unit \& integration testing, concurrent transaction
                                    correctness, edge-case coverage \\[2pt]
  \textbf{Observability}      & OpenTelemetry, Azure Monitor, Grafana, SLO/error-budget design,
                                on-call, incident response \\
\end{tabular}

\end{document}
