%──────────────────────────────────────────────────────────────────────────────
%  Liam Wood — Resume
%  Target: Senior Platform / Infrastructure Engineer — Big Tech
%  (Google, Meta, Apple, AWS, Stripe, Cloudflare)
%──────────────────────────────────────────────────────────────────────────────
\documentclass[11pt, letterpaper]{article}

\usepackage[top=0.55in, bottom=0.55in, left=0.70in, right=0.70in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

%── Colours ───────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{1A1A2E}
\definecolor{rule}{HTML}{888888}

%── Section style ─────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}\uppercase}
  {}{0em}{}
  [\vspace{-4pt}\textcolor{rule}{\hrule height 0.5pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{10pt}{4pt}

%── List style ────────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt,
  label=\textbullet
}

%── Helpers ───────────────────────────────────────────────────────────────────
\newcommand{\job}[3]{%
  \noindent\textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\pagestyle{empty}

%──────────────────────────────────────────────────────────────────────────────
\begin{document}

%── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{accent} Liam Wood}\\[4pt]
  Austin, TX \;|\;
  \href{tel:13057909093}{(305) 790-9093} \;|\;
  \href{mailto:general.lvwood@gmail.com}{general.lvwood@gmail.com}
\end{center}

\vspace{2pt}

%── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\job{Microsoft}{Software Engineer II — Platform Infrastructure {\normalfont\textit{(promoted twice in 3 years)}}}{July 2022 – Present}
\begin{itemize}
  \item Own design and end-to-end reliability of distributed event-processing infrastructure
    handling \textbf{6B+ events/month} across OneDrive and SharePoint, spanning dozens of
    interdependent services on Linux-hosted \textbf{AKS clusters}; define and enforce
    \textbf{SLOs and error budgets} with SRE teams.
  \item Architected \textbf{KEDA-driven autoscaling} tied to real-time queue depth and traffic
    patterns, eliminating over-provisioning waste and reducing tail latency
    (\textbf{\$500k–\$750k annual cost savings}).
  \item Owned \textbf{CI/CD pipelines} (Azure DevOps, Git) and progressive rollout tooling,
    improving release cadence from 6-week cycles to \textbf{weekly deployments} with integrated
    smoke testing and automated rollback.
  \item Led full \textbf{AKS migration} — authored \textbf{Terraform} modules for multi-region
    cluster provisioning, \textbf{Helm}-managed workloads, node pool autoscaling, and pod
    disruption budgets; rebuilt infra-as-code pipelines for safe, repeatable deploys at scale.
  \item Designed \textbf{multi-region failover} with Azure FrontDoor (anycast routing, TLS
    offload, WAF policies) and Traffic Manager; maintained \textbf{99.99\% availability}
    under continuous global load with automated BCDR runbooks and on-call rotation.
  \item Built \textbf{end-to-end observability} stack (Azure Monitor, Grafana, OpenTelemetry
    instrumentation); defined alerting thresholds, distributed tracing, and incident dashboards
    for a zero-downtime production system.
\end{itemize}

\vspace{4pt}

\job{Visa}{Senior Software Engineer — Clearing \& Settlement Infrastructure}{October 2020 – July 2022}
\begin{itemize}
  \item Designed and implemented \textbf{state-machine–driven settlement engine components}
    in Python and C++, processing \textbf{trillions in annual transaction volume} across
    distributed financial infrastructure.
  \item Engineered distributed systems requiring \textbf{fault-tolerant, exactly-once processing}
    under concurrent load; built early real-time transaction observability pipelines.
  \item Operated within a strict \textbf{Linux-based production environment}; diagnosed and
    resolved complex distributed failures with direct financial impact under time pressure.
\end{itemize}

\vspace{4pt}

\job{Digital Worlds Institute — University of Florida}{Software Developer}{August 2019 – February 2020}
\begin{itemize}
  \item Sole developer for a browser-based AR platform; built a \textbf{Node.js backend} with
    Redis pub/sub managing \textbf{100+ concurrent WebSocket connections} and real-time
    distributed state synchronization.
\end{itemize}

%── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\noindent\textbf{University of Florida} \hfill \textit{August 2018 – May 2022}\\
B.S.\ Computer Science\\[2pt]
Vice President, GatorVR — led technical workshops and mentored students in VR/AR
development and CS fundamentals.

%── Skills ────────────────────────────────────────────────────────────────────
\section{Skills}

\noindent
\begin{tabular}{@{}p{2.2in}p{4.5in}}
  \textbf{Languages}          & C++, Python, C\#/.NET, Node.js, JavaScript \\[2pt]
  \textbf{Infrastructure}     & Linux (AKS/bare-metal), Kubernetes, KEDA, Terraform, Helm,
                                Azure FrontDoor, Azure DevOps, BCDR Planning \\[2pt]
  \textbf{Distributed Systems}& High-scale event processing (6B+ events/month), multi-region
                                failover, fault-tolerant state machines, queue-based scheduling \\[2pt]
  \textbf{CI/CD \& Tooling}   & Azure DevOps, Git, progressive rollout, automated rollback,
                                smoke testing, integration \& regression testing \\[2pt]
  \textbf{Observability}      & OpenTelemetry, Azure Monitor, Grafana, distributed tracing,
                                SLO/error-budget design, alerting, on-call, incident response \\
\end{tabular}

\end{document}
